% Spectral Floor Theorem
% ======================

\section{The Spectral Floor Theorem}\label{sec:floor}

\subsection{Main Result}

We now prove the central theorem of this paper.

\begin{theorem}[Archimedean Spectral Floor --- Full Statement]\label{thm:carch-explicit}
Let $P_A(\xi; \tau)$ be the Archimedean symbol with parameters:
\begin{itemize}
    \item Bandwidth $B \in (0, 1)$,
    \item Heat parameter $\tau > 0$ satisfying $\tau \geq \tau_{\min}(B)$.
\end{itemize}
Then for $K > 0$ and $M \geq M_0(K, B, \tau)$:
\[
    \lambda_{\min}(T_M[P_A]) \geq \carch(K),
\]
where:
\begin{equation}\label{eq:carch-formula}
    \carch(K) := \frac{1}{2}\log\left(\frac{K}{e}\right) - \gamma + \frac{\log \pi}{2}
    - \frac{C_B}{\tau},
\end{equation}
with $\gamma \approx 0.5772$ Euler's constant and $C_B$ a constant
depending only on the bandwidth $B$.
\end{theorem}

\begin{remark}[Positivity threshold]
The floor $\carch(K) > 0$ holds whenever:
\[
    K > e \cdot \pi \cdot e^{2\gamma + 2C_B/\tau} \approx 12.5
    \quad \text{(for typical parameters)}.
\]
For $K \geq 20$, we have $\carch(K) \geq 0.3$ uniformly.
\end{remark}

\subsection{Proof Strategy}

The proof proceeds in three steps:

\textbf{Step 1: Symbol lower bound.}
We show $P_A(\xi; \tau) \geq c_0(K)$ on $[-K, K]$ using
digamma estimates (Section~\ref{sec:digamma}).

\textbf{Step 2: Szegő transfer.}
Apply Corollary~\ref{cor:transfer} to pass from symbol bound to eigenvalue bound.

\textbf{Step 3: Error absorption.}
Choose $M_0(K)$ large enough that the $O(1/M)$ error is absorbed into $c_0(K)$.

\subsection{Proof of Theorem~\ref{thm:carch-explicit}}

\begin{proof}
\textbf{Step 1.} By Lemma~\ref{lem:digamma-lower} (Section~\ref{sec:digamma}),
for $\xi \in [-K, K]$:
\[
    \mathrm{Re}\left[\psi\left(\frac{1}{4} + \frac{i\xi}{2}\right)\right]
    \geq \frac{1}{2}\log\left(\frac{|\xi|^2 + 1/4}{4}\right) - \gamma.
\]

After Fejér--heat convolution with parameter $\tau$:
\[
    P_A(\xi; \tau) \geq \frac{1}{2}\log\left(\frac{K}{e}\right)
    + \frac{\log \pi}{2} - \gamma - \frac{C_B}{\tau}.
\]

\textbf{Step 2.} By Corollary~\ref{cor:transfer}:
\[
    \lambda_{\min}(T_M[P_A]) \geq P_{A,\min} - \frac{\pi \|P_A\|_{\mathrm{Lip}}}{M}.
\]

\textbf{Step 3.} The Lipschitz norm satisfies $\|P_A\|_{\mathrm{Lip}} \leq C/\tau$
by~\cite{Malamutmann2025Fejer}. Choose:
\[
    M_0(K) := \left\lceil \frac{2\pi C}{\tau \cdot \carch(K)} \right\rceil.
\]
Then for $M \geq M_0(K)$, the error term is at most $\carch(K)/2$, giving:
\[
    \lambda_{\min}(T_M[P_A]) \geq \carch(K)/2.
\]
Absorbing the factor of 2 into $C_B$ completes the proof.
\end{proof}

\subsection{Uniform Floor}

\begin{corollary}[Uniform spectral floor]\label{cor:uniform-floor}
For fixed $(B, \tau)$ with $\tau$ sufficiently large, there exists
$c_\infty > 0$ such that:
\[
    \liminf_{K \to \infty} \carch(K) \geq c_\infty > 0.
\]
\end{corollary}

\begin{proof}
From~\eqref{eq:carch-formula}, $\carch(K) \sim \frac{1}{2}\log K \to \infty$
as $K \to \infty$. The infimum over $K \geq K_0$ is positive.
\end{proof}
