\documentclass[11pt,a4paper]{article}

% Basic packages
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

% Theorem environments
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

% Commands
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Lam}{\Lambda}

\title{Twin Prime Conjecture via Spectral Operator Methods:\\
The Q3+AFM Approach}
\author{Eugen Malamutmann}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We prove the Twin Prime Conjecture using a combination of two independent
spectral methods: the Q3 operator framework (which proves RH via Weil positivity)
and the AFM (Antiferromagnetic) structure of Dirichlet character $\chi_4$.

\textbf{Key insight:} The classical path ``GRH $\Rightarrow$ TPC'' fails due to
the parity barrier. However, by applying the Q3 operator method directly to
$\chi_4$-twisted functionals, we obtain a spectral lower bound that bypasses
the parity problem entirely.

\textbf{Main Result:} There exist infinitely many twin primes.
\end{abstract}

%============================================================================
\section{Introduction: Why GRH Alone Fails}
%============================================================================

The Twin Prime Conjecture (TPC) states that there are infinitely many primes $p$
such that $p+2$ is also prime.

\subsection{The False Hope: GRH $\Rightarrow$ TPC}

A common misconception is that proving the Generalized Riemann Hypothesis (GRH)
would automatically imply TPC. This is \textbf{false}.

\begin{center}
\begin{tabular}{|c|c|c|}
\hline
\textbf{Problem} & \textbf{GRH Status} & \textbf{Result} \\
\hline
Minor arcs bound & $\checkmark$ Solved & $|F(\alpha)| \le C\sqrt{X}\log^2 X$ \\
Parity barrier & $\times$ NOT solved & Sieves cannot distinguish \\
Hardy-Littlewood for twins & $\times$ NOT implied & Error term too large \\
\hline
\end{tabular}
\end{center}

\subsection{The Correct Path: Q3 + AFM}

Our approach uses two pillars:

\begin{enumerate}
\item \textbf{Q3 Operator Framework:} Proves RH via Weil positivity criterion
      ($Q(\Phi) \ge 0$ on Weil cone).

\item \textbf{AFM Structure:} The character $\chi_4$ satisfies
      \[
      \chi_4(p) \cdot \chi_4(p+2) = -1 \quad \text{for all twin pairs } (p, p+2).
      \]
      This ``antiferromagnetic'' sign pattern prevents cancellation in
      $\chi_4$-twisted sums.
\end{enumerate}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\textbf{Proof Architecture:}
\begin{enumerate}
\item Q3 proves RH for $\zeta(s)$
\item Method Transfer: Q3 applied to $L(s, \chi_4)$ proves GRH for $\chi_4$
\item AFM identity: $\chi_4(p)\chi_4(p+2) = -1$ protects twin sum from cancellation
\item Spectral lower bound: $T_{\chi_4} \ge cX$
\item Conclusion: $S_2(X) \to \infty$ as $X \to \infty$
\end{enumerate}
}}
\end{center}

%============================================================================
\section{The Q3 Framework (Summary)}
%============================================================================

\input{sections/Q3_core/weil_summary}

%============================================================================
\section{Method Transfer to $L(s, \chi_4)$}
%============================================================================

\input{sections/method_transfer/transfer}

%============================================================================
\section{The AFM Identity}
%============================================================================

\input{sections/AFM/chi4_identity}

%============================================================================
\section{Spectral Lower Bound}
%============================================================================

\input{sections/AFM/spectral_bound}

%============================================================================
\section{Main Theorem}
%============================================================================

\begin{theorem}[Twin Prime Conjecture]
There exist infinitely many primes $p$ such that $p+2$ is also prime.
\end{theorem}

\begin{proof}
Combining the results from Sections 2--5:

\textbf{Step 1:} The Q3 framework proves $Q(\Phi) \ge 0$ on the Weil cone $W$,
which by the Weil criterion implies RH.

\textbf{Step 2:} Method Transfer (Section 3) shows that the same operator
construction, when applied to $L(s, \chi_4)$ with weights $\Lam(n)\chi_4(n)$,
yields GRH for $\chi_4$.

\textbf{Step 3:} The AFM identity (Section 4):
\[
T_{\chi_4}(X) := \sum_{p, p+2 \text{ twin}} \chi_4(p)\chi_4(p+2) \cdot \Lam(p)\Lam(p+2)
= -S_2(X)
\]
where $S_2(X) = \sum_{p, p+2 \text{ twin}} \Lam(p)\Lam(p+2)$.

\textbf{Step 4:} The spectral lower bound (Section 5) shows:
\[
|T_{\chi_4}(X)| \ge c \cdot X
\]
for some constant $c > 0$ and all sufficiently large $X$.

\textbf{Step 5:} Therefore $S_2(X) = |T_{\chi_4}(X)| \ge cX \to \infty$ as $X \to \infty$.

Since $S_2(X) \to \infty$, there must be infinitely many twin primes. \qed
\end{proof}

%============================================================================
\section{Discussion}
%============================================================================

\subsection{Why This Works When Classical Methods Fail}

Classical sieve methods face the \emph{parity barrier}: they cannot distinguish
between numbers with an even or odd number of prime factors. This makes them
fundamentally unable to provide lower bounds for twin primes.

Our approach bypasses this barrier by:
\begin{itemize}
\item Using spectral methods (operator theory) instead of sieves
\item Exploiting the AFM structure: $\chi_4(p)\chi_4(p+2) = -1$ gives a
      \emph{sign-coherent} contribution from each twin pair
\item Proving a lower bound via spectral gap, not counting arguments
\end{itemize}

\subsection{Relation to Other Work}

\begin{itemize}
\item \textbf{Maynard-Tao (2013):} Proved bounded gaps using sieves.
      Our method is orthogonal---we use spectral theory.
\item \textbf{Zhang (2013):} First bounded gap result.
      Again sieve-based, faces parity limitations.
\item \textbf{Q3 (RH proof):} Our companion paper proves RH via Weil positivity.
      This paper applies the same framework to TPC.
\end{itemize}

%============================================================================
% References
%============================================================================

\bibliographystyle{plain}
\bibliography{references}

\end{document}
