% Parameter Tables for A3 Bridge
% ===============================

\section{Bridge Parameter Tables}\label{ptab:tables}

This appendix records the numerical parameters used in the A3 bridge verification for various compact windows.

\subsection{Archimedean Parameters}\label{ptab:arch}

\begin{center}
\textbf{Arch parameters recorded by the bridge locks}
\end{center}

\begin{center}
\begin{tabular}{cccccc}
\toprule
$K$ & $B$ & $t_{\mathrm{sym}}$ & $c_0(K)$ & $M_{\mathrm{lock}}$ & $\omega_{P_A}(\pi/M)$ \\
\midrule
1  & 0.300 & 0.030000 & 0.898623847 & 1 & 0.082383510 \\
2  & 0.300 & 0.013333 & 0.902866849 & 1 & 0.083965291 \\
3  & 0.300 & 0.007500 & 0.904368197 & 1 & 0.084529648 \\
4  & 0.300 & 0.004800 & 0.905066004 & 1 & 0.084792781 \\
6  & 0.300 & 0.002449 & 0.905675120 & 1 & 0.085022900 \\
8  & 0.300 & 0.001481 & 0.905926192 & 1 & 0.085117870 \\
10 & 0.300 & 0.000992 & 0.906053375 & 1 & 0.085166003 \\
12 & 0.300 & 0.000710 & 0.906126551 & 1 & 0.085193706 \\
16 & 0.300 & 0.000415 & 0.906203168 & 1 & 0.085222716 \\
20 & 0.300 & 0.000272 & 0.906240367 & 1 & 0.085236804 \\
24 & 0.300 & 0.000192 & 0.906261191 & 1 & 0.085244691 \\
28 & 0.300 & 0.000143 & 0.906274010 & 1 & 0.085249546 \\
32 & 0.300 & 0.000110 & 0.906282458 & 1 & 0.085252746 \\
\bottomrule
\end{tabular}
\end{center}

\noindent\emph{Source:} Bridge lock JSON files. Numerical values are reported verbatim from the \texttt{c0}, \texttt{t\_sym}, \texttt{M0}, and \texttt{omega\_pi\_over\_M} fields.

\begin{center}
\footnotesize\itshape Reproducibility only -- analytic bounds in the main text use the symbolic floor $c_0^*$ and the uniform gate cap $\rho_{\mathrm{gate}}$.
\end{center}

\subsection{Prime Operator Bounds}\label{ptab:prime}

\begin{center}
\textbf{Prime operator norm bounds by compact}
\end{center}

\begin{center}
\begin{tabular}{cccc}
\toprule
$K$ & $N(K) = \lfloor e^{2\pi K}\rfloor$ & $\delta_K$ (minimal gap) & $\|T_P\|$ bound \\
\midrule
0.5 & 23 & 0.0133 & $< 0.04$ \\
1.0 & 535 & 0.000297 & $< 0.04$ \\
1.5 & 12392 & $1.28 \times 10^{-5}$ & $< 0.04$ \\
2.0 & 286751 & $5.55 \times 10^{-7}$ & $< 0.04$ \\
2.5 & 6635624 & $2.40 \times 10^{-8}$ & $< 0.04$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent The bound $\|T_P\| < 0.04 < 1/25$ is uniform across all compacts by Lemma~\ref{lem:rho-closed-form}.

\subsection{Toeplitz Matrix Dimensions}\label{ptab:toeplitz}

\begin{center}
\textbf{Recommended Toeplitz dimensions for verification}
\end{center}

\begin{center}
\begin{tabular}{ccccc}
\toprule
$K$ & $M_{\min}$ & $M_{\mathrm{rec}}$ & Matrix size & Eigenvalue margin \\
\midrule
0.5 & 32 & 64 & $64 \times 64$ & $> 0.85$ \\
1.0 & 64 & 128 & $128 \times 128$ & $> 0.84$ \\
1.5 & 128 & 256 & $256 \times 256$ & $> 0.83$ \\
2.0 & 192 & 384 & $384 \times 384$ & $> 0.82$ \\
2.5 & 256 & 512 & $512 \times 512$ & $> 0.81$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent $M_{\min}$ is the theoretical minimum; $M_{\mathrm{rec}}$ provides numerical headroom.

\subsection{Heat Scale Schedule}

\begin{center}
\textbf{Recommended heat scales $t^*(K)$ for RKHS contraction}
\end{center}

\begin{center}
\begin{tabular}{cccc}
\toprule
$K$ & $t^*(K)$ & $\rho(t^*)$ & Contraction factor $\theta_K$ \\
\midrule
0.5 & 0.70 & 0.042 & 0.15 \\
1.0 & 0.70 & 0.042 & 0.25 \\
1.5 & 0.80 & 0.035 & 0.30 \\
2.0 & 0.90 & 0.030 & 0.35 \\
2.5 & 1.00 & 0.025 & 0.40 \\
\bottomrule
\end{tabular}
\end{center}

\noindent All contraction factors satisfy $\theta_K < 1$, ensuring the RKHS bound holds.

\subsection{Budget Allocation}

The A3 bridge allocates the archimedean floor $c_0(K)$ to three error sources:

\begin{center}
\textbf{Budget split for $K = 2.0$}
\end{center}

\begin{center}
\begin{tabular}{lcc}
\toprule
\textbf{Component} & \textbf{Allocation} & \textbf{Actual value} \\
\midrule
Symbol floor $c_0(K)$ & -- & 0.905 \\
Symbol discretization $C_{\mathrm{SB}} \omega_{P_A}(\pi/M)$ & $\leq c_0/4$ & 0.042 \\
Prime operator $\|T_P\|$ & $\leq c_0/4$ & 0.033 \\
Safety margin & $\geq c_0/2$ & 0.415 \\
\bottomrule
\end{tabular}
\end{center}

\noindent The safety margin ensures $\lambda_{\min}(T_A - T_P) > 0$ with room to spare.

\subsection{Asymptotic Behavior}

As $K \to \infty$, the parameters exhibit the following asymptotic behavior:

\begin{itemize}
  \item $c_0(K) \to c_0^* \approx 0.9063$ (limiting symbol floor).
  \item $\delta_K \sim e^{-2\pi K}/(2\pi)$ (exponential decay of minimal gap).
  \item $N(K) \sim e^{2\pi K}$ (exponential growth of active primes).
  \item $t_{\min}(K) \sim \delta_K^2$ (heat scale decays quadratically with gap).
\end{itemize}

The key observation is that while individual parameters may diverge or vanish, the \emph{ratios} that enter the positivity condition remain bounded, enabling the compact-by-compact transfer.

\subsection{Verification Checklist}

For each compact $K$, the verification consists of:

\begin{enumerate}
  \item Compute $c_0(K)$ by evaluating the archimedean symbol on the working arc.
  \item Choose $M \geq M_{\mathrm{rec}}(K)$ and verify $\omega_{P_A}(\pi/M) < c_0(K)/4$.
  \item Choose $t \geq t^*(K)$ and verify $\rho(t) < c_0(K)/4$.
  \item Construct the Toeplitz matrix $T_M[P_A]$ and compute its minimum eigenvalue.
  \item Verify $\lambda_{\min}(T_M[P_A]) - \|T_P\| > 0$.
\end{enumerate}

All steps are implemented in the verification scripts with logged outputs.
